---
title: "QR Codes"
format: html
eval: FALSE
---

# Setup Code

```{r}
library(qrcode)
```

```{r}
QR_Helper <- function(url, output, filename){

code <- qr_code(url)

TheFileName  <- paste0(filename, ".svg")

StoreHere <- file.path(output, TheFileName)

generate_svg(code, filename = StoreHere)
#plot(code)
}
```

# GitHub Repository

# GitHub Repository

[Link](https://github.com/DavidRach/FlowAwareness_Cyto2026)

```{r}
QR_Helper(url="https://github.com/DavidRach/AlphaBeta_Cyto2026",
    output="outputs", 
    filename="AlphaBetaRepo")
```


# AutoSpectral Walk-Through

```{r}

QR_Helper(url="https://umgcccfcsr.github.io/CytometryInR/course/community/AutoSpectral/",
    output="outputs", 
    filename="AutoSpectralWalkThrough")
```

# AutoSpectral GitHub

```{r}

QR_Helper(url="https://github.com/DrCytometer/AutoSpectral",
    output="outputs", 
    filename="AutoSpectralRepo")
```

# TRU-OLS Walk-Through

```{r}

QR_Helper(url="https://umgcccfcsr.github.io/CytometryInR/course/community/TRU-OLS/",
    output="outputs", 
    filename="TRU-OLS WalkThrough")
```

# TRU-OLS GitHub

```{r}

QR_Helper(url="https://github.com/De-Novo-Research/TRU-OLS",
    output="outputs", 
    filename="TRUOLSGitHub")
```

# PeacoQC

```{r}
QR_Helper(url="https://github.com/saeyslab/peacoQC",
    output="outputs", 
    filename="PeacoQCRepo")
```

# PeacoQC Vignette

```{r}

QR_Helper(url="https://www.bioconductor.org/packages/release/bioc/vignettes/PeacoQC/inst/doc/PeacoQC_Vignette.pdf",
    output="outputs", 
    filename="PeacoQCVignette")
```

```{r}
QR_Helper(url="https://crates.io/crates/peacoqc-cli",
    output="outputs", 
    filename="RustyPeacoQC")
```


# FlowAI

```{r}

QR_Helper(url="https://github.com/giannimonaco/flowAI",
    output="outputs", 
    filename="FlowAIRepo")
```

# FlowAI Vignette

```{r}

QR_Helper(url="https://www.bioconductor.org/packages/release/bioc/vignettes/flowAI/inst/doc/flowAI.html",
    output="outputs", 
    filename="FlowAIVignette")
```

# flowGate

```{r}

QR_Helper(url="https://github.com/DavidRach/flowGate",
    output="outputs", 
    filename="FlowGateRepoFork")
```

# flowGate WalkThrough

```{r}

QR_Helper(url="https://umgcccfcsr.github.io/CytometryInR/course/08_WaysToGate/#manual---flowgate",
    output="outputs", 
    filename="FlowGateWalkThrough")
```

# openCyto Repo

```{r}

QR_Helper(url="https://github.com/RGLab/openCyto",
    output="outputs", 
    filename="openCytoRepo")
```



# openCyto Walkthrough

```{r}

QR_Helper(url="https://umgcccfcsr.github.io/CytometryInR/course/08_WaysToGate/#automated---opencyto",
    output="outputs", 
    filename="openCytoWalkthrough")
```

# flowMagic Repo

```{r}

QR_Helper(url="https://github.com/semontante/flowMagic",
    output="outputs", 
    filename="flowMagicRepo")
```



# flowMagic Vignette

```{r}

QR_Helper(url="https://github.com/semontante/flowMagic/blob/main/pk_manual/flowMagic_manual.pdf",
    output="outputs", 
    filename="flowMagicManual")
```

# In: FlowJo to R

```{r}

QR_Helper(url="https://umgcccfcsr.github.io/CytometryInR/course/05_GatingSets/#cytoml",
    output="outputs", 
    filename="CytoMLWalkthrough")
```


# Out: R to FlowJo

```{r}

QR_Helper(url="https://umgcccfcsr.github.io/CytometryInR/course/08_WaysToGate/GStoFlowJo.html",
    output="outputs", 
    filename="CytoMLOut")
```

# DataForStatsWalks

```{r}

QR_Helper(url="https://umgcccfcsr.github.io/CytometryInR/course/11_DataForStats/",
    output="outputs", 
    filename="DataForStats")
```

# Subset Export

```{r}

QR_Helper(url="https://umgcccfcsr.github.io/CytometryInR/course/10_Downsampling/#export",
    output="outputs", 
    filename="ExportBypass")
```

# GatingSets

```{r}

QR_Helper(url="https://umgcccfcsr.github.io/CytometryInR/course/05_GatingSets/",
    output="outputs", 
    filename="GatingSets")
```

# flowWorkspace

```{r}

QR_Helper(url="https://github.com/RGLab/flowWorkspace",
    output="outputs", 
    filename="flowWorkspaceRepo")
```

# CytoML repo

```{r}

QR_Helper(url="https://github.com/RGLab/CytoML",
    output="outputs", 
    filename="CytoMLrepo")
```

# Coereba Repo

```{r}

QR_Helper(url="https://github.com/DavidRach/Coereba",
    output="outputs", 
    filename="CoerebaRepo")
```

# Coereba Vignette

```{r}

QR_Helper(url="https://davidrach.github.io/Coereba/articles/Workflow.html",
    output="outputs", 
    filename="CoerebaVignette")
```

# Bioconductor SummarizedExperiment

```{r}

QR_Helper(url="https://www.bioconductor.org/packages/release/bioc/vignettes/SummarizedExperiment/inst/doc/SummarizedExperiment.html",
    output="outputs", 
    filename="SummarizedExperiment")
```

# CytoNorm Repo

```{r}

QR_Helper(url="https://github.com/saeyslab/cytonorm",
    output="outputs", 
    filename="CytoNormRepo")
```

# CytoNorm Vignette

```{r}

QR_Helper(url="https://github.com/saeyslab/CytoNorm/tree/master/vignettes",
    output="outputs", 
    filename="CytoNormVignettes")
```

# CyCombine Repo

```{r}

QR_Helper(url="https://github.com/biosurf/cyCombine",
    output="outputs", 
    filename="cyCombineRepo")
```

# CyCombine Vignette

```{r}

QR_Helper(url="https://biosurf.org/cyCombine",
    output="outputs", 
    filename="CyCombineVignettes")
```

# FlowSOM Repo

```{r}

QR_Helper(url="https://github.com/saeyslab/FlowSOM",
    output="outputs", 
    filename="FlowSOMRepo")
```

# FlowSOM Vignette

```{r}

QR_Helper(url="https://www.bioconductor.org/packages/release/bioc/vignettes/FlowSOM/inst/doc/FlowSOM.pdf",
    output="outputs", 
    filename="flowSOMVignette")
```


# UWOT Repo

```{r}

QR_Helper(url="https://github.com/jlmelville/uwot",
    output="outputs", 
    filename="uwotRepo")
```

# PaCMAP Repo

```{r}

QR_Helper(url="https://github.com/YingfanWang/PaCMAP",
    output="outputs", 
    filename="PaCMAPRepo")
```

# Luciernaga UMAP and PACMAP

```{r}

QR_Helper(url="https://davidrach.github.io/Luciernaga/articles/DimensionalityVisualization.html#utility_umap",
    output="outputs", 
    filename="DimensionalityWrapperLuciernaga")
```

# Luciernaga Repo

```{r}

QR_Helper(url="https://github.com/DavidRach/Luciernaga/",
    output="outputs", 
    filename="LuciernagaRepo")
```

# Luciernaga Vignette

```{r}

QR_Helper(url="https://davidrach.github.io/Luciernaga/articles/FluorescenceSignatures.html#luciernaga_qc",
    output="outputs", 
    filename="LuciernagaQCVignette")
```

# Dashboard

```{r}

QR_Helper(url="https://umgccfcss.github.io/InstrumentQC/",
    output="outputs", 
    filename="Dashboard")
```

# 5LLevey

```{r}

QR_Helper(url="https://umgccfcss.github.io/InstrumentQC/Aurora5L.html",
    output="outputs", 
    filename="5L_Levey")
```

# 5L_History

```{r}

QR_Helper(url="https://umgccfcss.github.io/Aurora5L/",
    output="outputs", 
    filename="5L_History")
```

# How to InstrumentQC

# 5LLevey

```{r}

QR_Helper(url="https://davidrach.github.io/InstrumentQC_Install/",
    output="outputs", 
    filename="HowToInstrumentQC")
```


# CordBloodILT

```{r}

QR_Helper(url="https://www.frontiersin.org/journals/immunology/articles/10.3389/fimmu.2025.1628145/full",
    output="outputs", 
    filename="CordBloodILT")
```





